On The Impact of Atoms of Confusion in JavaScript Code

### 2021-10-06 3_Method.tex
Updates from Overleaf
final review
rephrase one of the interview questions

\subsubsection*{Interview Process} We conducted semi-structured interviews using a web conferencing software. We recorded all the interviews with the consent of the participants. On average, the interviews lasted 26.29 minutes, with the shortest one lasting 14.59 minutes and the longest one 43.06 minutes.

%In the interviews we presented developers with two functionally equivalent short programs, one with a single atom and another one without the atom, differed concerning program comprehension. We then asked them to tell us which program was easier to understand. 
%The main goal of the interviews was to have developers assess whether two functionally equivalent short programs, one with a single atom and another one without the atom, differed concerning program comprehension, and, if so, which version they regarded as the easier one to understand.

Two of the researchers conducted the interviews, and a third one listened to all the recordings to cross-validate the collected data.
The interviews had three main parts. In the first one, we asked the developers the following demographic information: name, email, gender, level of education, current job position, JavaScript experience in years and other programming languages they have worked with.
Table \ref{pinterview} summarizes this demographic information.

\begin{table}[htb!]
  \centering
\begin{scriptsize}  
\begin{tabular}{clcl}
\toprule
ID & Education & JS Experience & Other Languages \\ \midrule 
P1 & BSc Degree & 9 years & Java, PHP, C, Go  
\\ 
P2 & HS Degree & 3 years & Python, Go, Dart, Lua, C++, C\#
\\ 
P3 & BSc Degree & 4 years & Java, C
\\ 
P4 & Undergraduate & 3 years & Python, C, C++, Java, Go
\\ 
P5 & Master Student & 3 years & Python, SQL
\\ 
P6 & Bsc Degree & 15  years  & Java, PHP, C, Python , Ruby, C\# and R
\\ 
P7 & BSc Degree  & 6 years & C, C++, Java, Assembly, Kotlin
\\ 
P8 & PhD Degree & 2 years & Java, Python
\\ 
P9 & BSc Degree  & 5 years & PHP
\\ 
P10 & Master Student & 4 years & Java, C\# and Python
\\ 
P11 & Master Student & 4 years & Java, Erlang, C\#, Cobol
\\ 
P12 & Master Degree & 1 year & C
\\ 
P13 & Master Degree & 13 years & Java, PHP
\\ 
P14 & Master Student & 3 years & C, Python, Ruby
\\ 
P15 &  BSc degree  & 2 years & Java, PHP
\\ \bottomrule
\end{tabular}
\end{scriptsize}
    \caption{Demographic information of the participants}
    \label{pinterview}
\end{table}

In the second part of the interview our aim was to allow the subjects to describe their JavaScript experience, as well as to allow them to reveal any JavaScript constructs they regarded as innately confusing. This would allow us to identify potential atom candidates that are more specific to the JavaScript language. Examples of questions we explored in this section include: \emph{Do you think JavaScript is a language that produces code that is hard to understand?} and \emph{Do you regard any particular construct or idiom of the language as
  especially confusing?}

@@

\begin{table}[ht]
  \centering
  \begin{scriptsize}
 \begin{tabular}{rrrrr}
   \hline
                       & Min.             & Median        & Mean             & Max. \\ \hline
 Lines of Code         & \num{5543}       & \num{36161.5} & \num{111432.33}  & \num{1278405} \\
 Num. of Forks         & \num{1244}       & \num{6078}    & \num{8906.24}    & \num{68849} \\
 Num. of Contributors  & \num{6}          & \num{285.5}   & \num{533.44}     & \num{4047} \\
 Num. of Stars         & \num{23672}      & \num{34990}   & \num{46919.51}   & \num{310935} \\

    \hline
 \end{tabular}
 \end{scriptsize}
 \caption{Some descriptive statistics about the projects used in the MSR study}
 \label{tab:projects-statistics} 
 \end{table}

>>>>

\subsubsection*{Interview Process} We conducted semi-structured interviews using a web conferencing software. We recorded all the interviews with the consent of the participants. On average, the interviews lasted 26.29 minutes, with the shortest one lasting 14.59 minutes and the longest one 43.06 minutes. 
Two of the researchers conducted the interviews, and a third one listened to all the recordings to cross-validate the collected data.
The interviews had three main parts. In the first one, we asked the developers the following demographic information: name, email, gender, level of education, current job position, JavaScript experience in years and other programming languages they have worked with.
Table \ref{pinterview} summarizes this demographic information.

\begin{table}[htb!]
  \centering
  \caption{Demographic information of the participants}
\begin{scriptsize}  
\begin{tabular}{clcl}
\toprule
ID & Education & JS Experience & Other Languages \\ \midrule 
P1 & BSc Degree & 9 years & Java, PHP, C, Go  
\\ 
P2 & HS Degree & 3 years & Python, Go, Dart, Lua, C++, C\#
\\ 
P3 & BSc Degree & 4 years & Java, C
\\ 
P4 & Undergraduate & 3 years & Python, C, C++, Java, Go
\\ 
P5 & Master Student & 3 years & Python, SQL
\\ 
P6 & Bsc Degree & 15  years  & Java, PHP, C, Python , Ruby, C\# and R
\\ 
P7 & BSc Degree  & 6 years & C, C++, Java, Assembly, Kotlin
\\ 
P8 & PhD Degree & 2 years & Java, Python
\\ 
P9 & BSc Degree  & 5 years & PHP
\\ 
P10 & Master Student & 4 years & Java, C\# and Python
\\ 
P11 & Master Student & 4 years & Java, Erlang, C\#, Cobol
\\ 
P12 & Master Degree & 1 year & C
\\ 
P13 & Master Degree & 13 years & Java, PHP
\\ 
P14 & Master Student & 3 years & C, Python, Ruby
\\ 
P15 &  BSc degree  & 2 years & Java, PHP
\\ \bottomrule
\end{tabular}
\end{scriptsize}
    \label{pinterview}
\end{table}

In the second part of the interview our aim was to allow the subjects to describe their JavaScript experience, as well as to allow them to reveal any JavaScript constructs they regarded as innately confusing. This would allow us to identify potential atom candidates that are more specific to the JavaScript language. Examples of questions we explored in this section include: \emph{Does JavaScript favor developers to produce code that is hard to understand?} and \emph{Do you regard any particular construct or idiom of the language as
  especially confusing?}

@@

\begin{table}[ht]
  \centering
   \caption{Some descriptive statistics about the projects used in the MSR study}
  \begin{scriptsize}
 \begin{tabular}{rrrrr}
   \hline
                       & Min.             & Median        & Mean             & Max. \\ \hline
 Lines of Code         & \num{5543}       & \num{36161.5} & \num{111432.33}  & \num{1278405} \\
 Num. of Forks         & \num{1244}       & \num{6078}    & \num{8906.24}    & \num{68849} \\
 Num. of Contributors  & \num{6}          & \num{285.5}   & \num{533.44}     & \num{4047} \\
 Num. of Stars         & \num{23672}      & \num{34990}   & \num{46919.51}   & \num{310935} \\

    \hline
 \end{tabular}
 \end{scriptsize}
 \label{tab:projects-statistics} 
 \end{table}
